Merge_PICO_Growth_PUR

### 2024-01-18 Code/Merge_GrowthPURData.Rmd
Removed unneccesary libraries

```{r load libraries, include=FALSE}
# libraries; Note check actual dependencies
library(tidyverse)
library(lubridate)
library(broom)
library(knitr)

knitr::write_bib(c("tidyverse", "lubridate","knitr", "broom", "zoo", "RColorBrewer", "grid", "glue", "bookdown"), 'RPackages.bib')

>>>>

```{r load libraries, include=FALSE}

library(lubridate)
library(broom)
library(knitr)
library(tidyverse)
